\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, pdfpages, pdflscape, lscape, color, listings, hyperref, amssymb,graphicx,textcomp,varioref,afterpage,subcaption, float} 

\setlength\topmargin{-0,5in}
\setlength\textheight{9in}

\usepackage[margin=2.5cm]{geometry}

\newcommand{\Fig}[1]{Figure \ref{#1}}
\newcommand{\fig}[1]{figure \ref{#1}}
\newcommand{\tab}[1]{table \ref{#1}}
\newcommand{\eq}[1]{equation \ref{#1}}
\newcommand{\Eq}[1]{Equation \ref{#1}}
\newcommand{\alg}[1]{algorithm \ref{#1}}
\newcommand{\Alg}[1]{Algorithm \ref{#1}}
\newcommand{\chp}[1]{chapter  \ref{#1}}
\newcommand{\Chp}[1]{Chapter  \ref{#1}}
\newcommand{\e}[1]{\cdot 10^{#1}}
\newcommand{\h}{\hbar}
\newcommand{\der}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\dder}[2]{\frac{\partial^2 #1}{\partial #2^2}}

%opening
\title{Abstracts Geilo Winter School}
\author{Simen Tennøe and Jonathan Feinberg}

\begin{document}
\maketitle
\newpage


% tydligere titler med PCE in front
\section{Polynomial chaos expansion part II: Method Introduction}

Polynomial chaos expansion is a class of methods for determining the
uncertainties in forward models given uncertainty in input parameters.
% Mangler en setning om hvorfor PCE har noe verdi (svar: den er raskere enn andre metoder)
In this first lecture we will give an introduction to the general
concepts necessary to understand the foundation of the theory.
Along the lecture will also give an introduction to a software
package called Chaospy, a Python toolbox developed specifically to
use polynomial chaos expansion in practice.



\section{Polynomial chaos expansion part II: Practical implementation}
% Mangler setning om at dette er hvor man lærer å bruke PCE på praktiske problemer.
One important set of methods to get the coefficients of the
polynomial chaos expansion are collocation methods.
These are methods that require the residue of the governing
equations to be zero at specific points in the computations.
% hva var dette? ser litt ut som Galerkin.
We will take a closer look at two subclasses of this set of
methods, the pseudospectral approach utilizing sparse grids and a
interpolation approach.  After this lecture you will be able to do
a polynomial chaos expansion using Chaospy on simpler problems.

% Pseudo-spectral methods collocation



\section{Polynomial chaos expansion part III: Some advanced topics}
One of the assumption when constructing a polynomial chaos
expansion is that the input distribution consist of stochastically
independent components.
In the first half of this lecture, we will take a look at what
happens when this assumption does not hold.
In the second half we will end with a walkthrough of the Galerkin
method, another often used method for finding the coefficients of a
generalized polynomial chaos expansion.



\end{document}
